Learning Discrete-valued Bayesian Networks from Mixed Data

### 2015-11-25 BN_discretizer_paper.tex
Find typo

\noindent
The discretization policy discretizes $\cX$ into $k$ intervals.
Let the samples of $\cX$ in a given dataset $D$ be sorted in ascending order, ${\cx_{1:n} = \curly{\cx_1 \leq \cx_2 \leq \ldots \leq \cx_n}}$, and let the unique values be ${\cu_{1:m} = \curly{\cu_1 \leq \cu_2 \leq \ldots \leq \cu_{m}}}$.
The index of the last occurence of $\cu_i$ in $\cx_{1:n}$ is denoted $s_i$.

@@

\begin{small}
\begin{equation}
\label{eq:BayesianScore}
  \ln P(D\mid G) = \ln P(G) + \sum_{i=1}^N \sum_{j=1}^{q_i} \ln \paren{
    \frac{
      \mathrm{\Gamma}\paren{\alpha_{ij}^{(0)}}
    }{
      \mathrm{\Gamma}\paren{\alpha_{ij}^{(0)} + \beta_{ij}^{(0)}}
    }
  } + \sum_{k=1}^{r_i} \ln \paren{
    \frac{
      \mathrm{\Gamma}\paren{\alpha_{ij}^{(k)} + \beta_{ij}^{(k)}}
    }{
      \mathrm{\Gamma}\paren{\alpha_{ij}^{(k)}}
    }
  }\text{,}
\end{equation}
\end{small}

>>>>

\noindent
The discretization policy discretizes $\cX$ into $k$ intervals.
Let the samples of $\cX$ in a given dataset $D$ be sorted in ascending order, ${\cx_{1:n} = \curly{\cx_1 \leq \cx_2 \leq \ldots \leq \cx_n}}$, and let the unique values be ${\cu_{1:m} = \curly{\cu_1 < \cu_2 < \ldots < \cu_{m}}}$.
The index of the last occurence of $\cu_i$ in $\cx_{1:n}$ is denoted $s_i$.

@@

\begin{small}
\begin{equation}
\label{eq:BayesianScore}
  \ln P(G\mid D) = \ln P(G) + \sum_{i=1}^N \sum_{j=1}^{q_i} \ln \paren{
    \frac{
      \mathrm{\Gamma}\paren{\alpha_{ij}^{(0)}}
    }{
      \mathrm{\Gamma}\paren{\alpha_{ij}^{(0)} + \beta_{ij}^{(0)}}
    }
  } + \sum_{k=1}^{r_i} \ln \paren{
    \frac{
      \mathrm{\Gamma}\paren{\alpha_{ij}^{(k)} + \beta_{ij}^{(k)}}
    }{
      \mathrm{\Gamma}\paren{\alpha_{ij}^{(k)}}
    }
  }\text{,}
\end{equation}
\end{small}
